\vspace{30mm} {\Large\bf RISC-V Duo-PLIC for the Advancced Interrupt Architecture} \\ {\large Document Version \DuoPLICRev}

### 2023-06-08 doc/src/IOMMU.tex
Added clarification about the term IOMMU
Signed-off-by: David Kruckemyer <dkruckemyer@ventanamicro.com>
Signed-off-by: Anup Patel <apatel@ventanamicro.com>

This chapter is concerned only with how an \mbox{IOMMU} recognizes and
processes MSIs directed to virtual machines.
Most other functions and details of an \mbox{IOMMU} are beyond the scope of
this standard, and must be specified elsewhere.

>>>>

This chapter uses the term \mbox{IOMMU} in a generic sense that encompasses
all translation and transaction processing services required to virtualize
device accesses and is concerned only with how an \mbox{IOMMU} recognizes
and processes MSIs directed to virtual machines. Most other functions and
details of an \mbox{IOMMU} are beyond the scope of this standard, and must
be specified elsewhere.

\begin{commentary}
The {\RISCV} \mbox{IOMMU} Architecture Specification provides a detailed
description of the \mbox{IOMMU} architecture, dividing translation and
transaction processing functionality into blocks such as \mbox{IOMMU},
\mbox{IO Bridge}, etc. and describing how those blocks are integrated
into a system.
\end{commentary}
